wgcna

### 2019-08-23 analysis/08_wgcna.Rmd
now with markdown
multiple wgcna plots

---
title: "wgcna"
output: html_document
---

@@

## hypothalas

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA("hypothalamus")

@@

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA("pituitary")
```

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA("gonad")
```

>>>>

---
title: "wgcna"
output: md_document
---

@@

## Females

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("female.gonad", "female.hypothalamus", "female.pituitary"))

@@

## Males

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"))
```

## hypothalamus

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.hypothalamus", "female.hypothalamus"))
```

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}
#subsetWGCNA(c("female.pitutary", "male.pitutary"))
```

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad", "male.gonad"))
```
